### 2017-01-22 thesis/intro/intro.tex
Finished obesity metagene direction subsection
Started editing introduction -- tmp commit

Obesity is defined as an abnormal or excessive fat accumulation that may impair health of that individual \citep{Garrow1988}.

One common and widely used approach to categorise individuals is by measuring the \gls{bmi} of the individual.
\gls{bmi} is a measurement based on the weight-to-height ratio of an individual that is used by clinicians and epidemiologists to classify adults into underweight, normal weight, overweight or obese categories.
The unit of \gls{bmi} is defined as the individual's weight in kilograms per square of the height in meters (kg/m$^2$).

@@

In addition to this, the worldwide prevalence of childhood overweight and obesity has been increasing steadily since 2000 \citep{WHO2014}.
Furthermore, the prevalence of overweight in children under 5 years was estimated to reach from 6.3\% in 2013 to 11\% by 2025 if the current trend continued \citep{WHO2014}.
The current obesity status of the adult population is bad already, but the fact that more of the younger population who are overweight and obese poses a much greater risk for the health of the population (discussed in \cref{sub:impact_of_obesity}).

@@

Until these terrible trends stop, and even after the trends stop, the world will need a plan to live along with this ongoing global epidemic of obesity and its associated diseases.

@@

Obesity is caused by continuous intake of food, whether they are controlled or not, without expending all of the energy gained.
The key to the problem is the control of food intake and energy expenditure, and how they are regulated in your body.

\subsubsection{Role of hypothalamus and arcuate nucleus in food intake control}
\label{ssub:role_of_hypothalamus_and_arcuate_nucleus_in_food_intake_control}

The central role of hypothalamus in the context of obesity is the control of satiety, and therefore food intake.
The hypothalamus receives both nueronal and hormonal inputs from the body and propagates the signal to the downstream neurons that ultimately affect the food intake of the individual \citep{Bell2005, Spiegelman2001}.

Within the hypothalamus, there is a group of neurons located within the arcuate nucleus that is essential for satiety signal transmission.
There are two types of neurons in the arcuate nucleus: orexogenic and anorexogenic neurons.
Orexogenic neurons are responsible for the promotion of food intake and reducing energy expenditure, whereas the anorexogenic neurons have the opposite effect \citep{Barsh2002}.

The orexogenic neurons produce \gls{npy} and \gls{agrp} which induces orexogenic signal to the downstream neurons; anorexogenic neurons produce \gls{pomc} and \gls{cart} which induces anorexogenic signal to the downstream neurons \citep{Barsh2002, Spiegelman2001}.
When stimulated by, for example, endocrine signals, these two different types of neurons act on the downstream neurons to promote or reduce food intake and energy expenditure.

\subsubsection{Leptin-melanocortin pathway}
\label{ssub:leptin_melanocortin_pathway}

Leptin-melanocortin pathway is the pathway in which the level of satiety is controlled and regulated.
In this pathway, both the orexogenic and anorexogenic neurons have crucial roles in controlling the satiety of the individual, and therefore their eating behaviour.

When a satiety-controlling hormone such as leptin reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both orexogenic and anorexogenic neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.\\

\noindent
Both \gls{pomc} and \gls{cart} are strong anorexogenic neuropeptides that stimulate the downstream effector neurons via the \gls{mc4r} pathway \citep{Barsh2002}.

\gls{pomc} is a precursor protein that is cleaved to produce \gls{acth}, $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin \citep{Smith1988}.
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

Similarly, \gls{cart} is also a neuropeptide that has a strong anorexogenic effect discovered by \citet{Kristensen1998}.
Unlike $\alpha$-MSH, the receptor for \gls{cart} has not been identified yet, and the exact mechanism in which \gls{cart} acts is unclear \citep{Kristensen1998, Rogge2008}.

Since the expression of both neuropeptides are under the control of leptin, and that $\alpha$-MSH is known to stimulate the melanocortin pathway to produce an anorexogenic signal to the downstream neurons, this satiety-controlling signalling pathway is known as the leptin-melanocortin pathway.
\\

\noindent
In contrast to the \gls{pomc}/\gls{cart} neurons, orexogenic neuropeptides \gls{npy} and \gls{agrp} are produced in the \gls{npy}/\gls{agrp} neurons when stimulated by hormones that control satiety.

\gls{npy} was first discovered by \citet{Tatemoto1982}, and later associated with altered eating behaviour in rats by \citet{Clark1984}.
\gls{npy} is recognised by the \gls{nyr1}, a G protein-coupled receptor expressed on the downstream effector neurons, which relays the orexogenic signal from the \gls{npy}/\gls{agrp} neurons \citep{Barsh2002, Bell2005, Herzog1992}

Agouti protein is a protein normally expressed in the skin where it affects the pigmentation, and was first identified over 100 years ago by \citet{Castle1910} in mice that had yellow, or agouti-coloured coat.
Although the fact that ubiquitous expression of agouti protein caused obesity in mice was known for a long time, the biochemical mechanism that caused such phenotype was not elucidated until 1997 by \citet{Ollmann1997}.
In brief, \gls{agrp} was shown to be a strong antagonist of the \gls{mc4r}, expressed in the downstream neurons to the \gls{npy}/\gls{agrp} neurons, and thus inhibited the anorexogenic signalling through the melanocortin pathway \citep{Barsh2002,Ollmann1997}.\\

\noindent
Together, \gls{npy}/\gls{agrp} and \gls{pomc}/\gls{cart} neurons produce contrasting signals that affect the overall satiety of the individual.
Depending on how strong or weak these signals are, the individual may be more or less susceptible to obesity.

\subsubsection{Role of hormones in leptin-melanocortin pathway}
\label{ssub:role_of_hormones_in_leptin_melanocortin_pathway}

There are many hormones in your body that regulates various physiological aspects of your body.
Out of the many, four hormones in particular have an important role in regulating the satiety of an individual: ghrelin, leptin, insulin, and \gls{pyy}.\\

\noindent
Ghrelin, originally identified as a peptide that stimulated the release of growth hormone from the pituitary, is a hormone produced mainly in the stomach that has a significant role in meal initiation and food intake, as well as energy homeostasis \citep{Kohno2003, Kojima1999, Nakazato2001}.
Ghrelin is known to be a ligand for the \gls{ghsr} which is expressed abundantly on the \gls{npy}/\gls{agrp} neurons, and increases the Ca$^{2+}$ concentration in these neurons \citep{Kohno2003}.

Furthermore, \citet{Seoane2003} showed that ghrelin increased the mRNA levels of both \gls{npy} and \gls{agrp} in these neurons and hence their protein expression, indicating the role of ghrelin as the orexogenic hormone that affects the overall outcome of the satiety signal.
\\

\noindent
Leptin, on the other hand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.
First identified by \citet{Zhang1994}, the dicovery of the leptin gene, followed by the discovery of leptin receptor gene by \citet{Tartaglia1995}, were probably the major breakthrough in the field of obesity research.

Leptin is produced and secreted mainly by the white adipose tissue, and the circulating concentration of leptin in the body is proportional to body fat stores \citep{Barsh2002, Moustafa2013, Zhang1994}.
Leptin receptor has many splice variants, but the long variant of the leptin receptor is highly expressed only in the hypothalamus \citep{Ghilardi1996, Lee1996}.
In addition to this, leptin receptor is expressed on both the \gls{npy}/\gls{agrp} and \gls{pomc}/\gls{cart} neurons, and have different effect on the outcome of the satiety signal depending on which neuron leptin stimulates.

In \gls{npy}/\gls{agrp} neuron, it has been shown to reduce the Ca$^{2+}$ concentration, antagonising the effect of ghrelin on this type of neurons \citep{Kohno2003}.
Furthermore, binding of leptin to the leptin receptor on the \gls{npy}/\gls{agrp} neuron causes a decreased release of \gls{gaba}, which inhibits the \gls{pomc}/\gls{cart} neuron \citep{Cowley2001}.

In \gls{pomc}/\gls{cart} neuron, binding of leptin to its recpetor causes a depolarisation of the neuron \citep{Cowley2001}.
Together with the indirect effect from the \gls{npy}/\gls{agrp} neuron, leptin promotes the \gls{pomc}/\gls{cart} neuron to release $\alpha$-\gls{msh}, and therefore sends a anorexogenic signal to its downstream effector neurons.
\\

\noindent
Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.

Briefly, when insulin binds to the insulin receptor, \gls{irs} protein family is recruited and phosphorylated by the insulin receptor's intrinsic tyrosine kinase activity \citep{Saltiel2002}.
The phosphorylated \gls{irs} protein then activates \gls{pi3k}, which in turn activates its downstream targets, causing a rapid signal cascade through the cell \citep{Saltiel2002}.

The evidence of insulin's involvement in the satiety control was not particularly clear; even though there were strong evidence of obesity with neuron-specific deletion of insulin receptor, and that the insulin level, like leptin, was proportional to the fat mass also suggested the role of insulin in satiety and body weight control \citep{Barsh2002, Bruning2000, Woods1979}.
This was perhaps due to the fact that leptin and insulin used two different signalling pathways in the cell: leptin used the \gls{jak}/\gls{stat} signalling pathway, whereas insulin used the \gls{pi3k} pathway for signalling \citep{Ghilardi1996}.
This was puzzling to the researchers as there seemed to be no converging point of the two hromones in these pathways.

However, leptin, and subsequently insulin, was shown to activate ATP-dep\-endent K$^+$ channel in glucose-responsive neurons in the hypothalamus \citep{Spanswick1997, Spanswick2000}.
The activation of K$^+$ channel provided evidence for the two pathways to act similarly on the cell, at least for an acute response, suggesting a convergence in the pathway response by the two hormones, and therefore their role in satiety control.
\\

\noindent
The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.

\gls{pyy} is a gut hormone that is secreted postprandially, and it is released at levels proportional to the calorie content of the meal \citep{Adrian1985}.
\gls{y2r} is an inhibitory presynaptic receptor that is highly expressed in the \gls{npy}/\gls{agrp} neuron, and is the target of the \gls{pyy} hormone \citep{Batterham2002}.
\citet{Batterham2002} showed that \gls{pyy} decreased the expression of \gls{npy} in the \gls{npy}/\gls{agrp} neuron, and activated the \gls{pomc}/\gls{cart} neuron by membrane depolarisation.
The two mechanisms of \gls{pyy} produces an anorexogenic signal and encourages the individual to stop eating.\\

\noindent
When any one of these neurons, neuropeptides, hormones or its corresponding receptors become defective, it can lead to some form of eating disorder (briefly covered in \cref{ssub:Individual-level_(micro-level)_factors}: \nameref{ssub:Individual-level_(micro-level)_factors}).
Therefore the roles of these neurons, neuropeptides, and hormones are crucial for healthy diet and body weight maintenance.

@@

There are many environmental factors associated with the global rise in obesity (discussed in \cref{ssub:Population-level_(macro-level)_factors}: \nameref{ssub:Population-level_(macro-level)_factors}).
Even though these environmental factors are probably the most significant contributor of the current global obesity epidemic, there are some individual-level, genetic factors that assist in the overall increase in the proportion of the population that are obese.

There are many evidence of obesity being caused by individual-level genetic factors that make some individuals more predisposed to obesity than others.
Generally speaking, there are two classes of genetically-driven obesity: monogenic obesity and polygenic obesity \citep{Moustafa2013}. \\

\noindent
Monogenic obesity is where a single mutation in one of the genes that is directly involved in the obesity pathway causes severe obesity in the individual.
Since these mutations are usually directly related to the key neurons/neuropeptides/hor\-mones that were mentioned earlier (\cref{sub:physiological_mechanism_of_obesity}), the resulting phenotype from the mutation causes severe early-onset obesity.
However, although these mutations cause a devastating effect on the individual, these mutations occur very rarely in the population.
With that said though, the identification of these mutations have shed light on the mechanisms in which obesity is developed and it is worth mentioning some of these mutations to highlight the importance of the components involved in the obesity pathway.

The first mutation that should be mentioned is in the leptin gene.
\citet{Montague1997} found a single nucleotide deletion mutation at position 133 of the leptin gene in children with early-onset obesity.
They further showed that the mutation caused a frameshift mutation in the protein, resulting in an inactive form of leptin that was not able to be secreted \citep{Montague1997}.

In close relation to this mutation is the mutation in the leptin receptor gene.
\citet{Clement1998} have discovered a single nucleotide substitution mutation that led to the leptin receptor transcript that skipped exon 16, leading to a form of the receptor with no transmembrane or intracellular domain.
Individuals with this rare mutation showed extreme hyperphagia and symptoms of early-onset obesity, even though their circulating leptin levels were present abundantly \citep{Clement1998}.

The next couple of mutations are associated with the synthesis and the processing of \gls{pomc}.
\citet{Krude1998} found single nucleotide mutations in the exonic region of the \gls{pomc} gene that affected the transcription of the $\alpha$-\gls{msh} region (and some other regions) of \gls{pomc}.
\citet{Jackson1997} identified a mutation in the \gls{pc1}, an enzyme responsible for the processing of many prohormones and neuropeptides, including \gls{pomc}.
In either case, the mutation resulted in the lack of $\alpha$-\gls{msh} in the neurons for satiety signalling and caused severe early-onset obesity.

As mentioned earlier, even though these mutations are very rare and affects only those individuals that have one of these mutations, it had a profound impact in the field of obesity research and contributed significantly to the knowledge of the mechanism of how obesity develops.
\\

% \citep{Farooqi2003}
% \citep{Kublaoui2006}
% \citep{Dubern2001}
% \citep{Challis2002}
% \\

\noindent
Polygenic obesity is where a combination of variants in multiple genes or multiple regions of the genome, together with environmental factors, causes obesity in the individual \citep{Moustafa2013}.
Unlike in monogenic obesity where a single mutation in a gene causes severe obesity, the variants in some of the genes or genomic regions involved in polygenic obesity have little effect on the individual's obesity status by itself, but in combination with many other variants, together with environmental factors, it has a serious effect on the individual.

Known as the ``thrifty gene'' hypothesis, \citet{Neel1962} suggested that the genes that were important in obesity have been around in the population for many generations, as it would have had a selective advantage in an environment where the population experienced starvation more frequently than the current generation.
However, as food became more accessible, a subset of the population who were particularly good at storing fat and survive the starvation period ``overreacted'' to this rapid change in the environment \citep{Bell2005, Spiegelman2001}.
These observations in the rise in obesity in subsets of population cannot be explained simply by external factors alone, and there is a significant genetic component involved in this phenomenon \citep{Bell2005}.

@@

Discovery of the \gls{fto} gene has lead to extensive research on the gene, and the mechanism of action by the \gls{fto} variant has been recently uncovered  from these efforts \citep{Claussnitzer2015a,Smemo2014a}.
The association between obesity and genetic variations, and their mechanisms that lead to obesity, has not been fully elucidated due to its complexity, but it may not be long before they are fully uncovered.

@@

Even though some individual-level factors are involved with obesity, it is clear that these individual-level factors cannot be accounted for the global epidemic of obesity that the world currently observes.
For this reason, obesity is thought to be caused mainly by the environmental factors that are present in the population.\\

\noindent
The first key factor that contirbutes to the global rise in the proportion of the population that is obese is the availability and abundance of certain food in the country.
With the help from government trade policies, food and other goods have become easier to trade between the country, helping the economic growth of many countries around the world \citep{Kearney2010}.
This led to greater abundance of food in general, greater number of choices of food and shifted the overall nutritional status of the country \citep{Malik2013}.
This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in a different, much larger problem -- obesity.

As an example, in the \gls{usa}, the cost of corn and soy is low due to the fact that they are the raw ingredients for most processed food and beverages, such as high fructose corn syrups used to sweeten many soft drinks in the \gls{usa} \citep{Malik2013}.
Moreover, corn and soy are also the main food for the livestock, which results in lower prices for meat \citep{Malik2013}.
On the othere hand, the prices of fruits and vegetables remain expensive due to the lack of support by the government to lower the cost associated with the production \citep{Malik2013}.

As a result, more people are inclined to consume food that are cheap, have little nutritional value and high in energy, than the food that are expensive, nutritional and healthy alternatives.
Thus, the population is more likely to become obese by making worst food choice.\\

\noindent
The second factor to consider is the behavioural changes led by the urbanisation of the population.
Urbanisation is defined as the gradual increase in the proportion of people living in urban areas.
As more people take up urban lifestyle, they are exposed to the new environment where there is a better range of food selection, as well as technological and mechanical advancement in transport and other daily chores that may not be available in rural areas where these people come from.

Although there are many advantages involved with urbanisation, such as access to developed health care systems, education and advanced technologies, the lifestyle change also impose negative health behaviour that ultimately lead to positive energy balance and therefore obesity \citep{Malik2013}.

Lack of physical activity is one of the obvious components that contribute to obesity, which is also linked with the urbanisation of the population.
Currently, the recommended amount of physical activity to keep an individual fit and healthy is $\geq$ 150 min of moderate-intensity aerobic physical activity per week, or $\geq$ 30 min of physical activity on most days of the week \citep{Pate1995, WHO2010}.
However, in many urban cities, this recommended level of physical exercise is difficult to achieve and maintain, due to the shift towards the sedentary behaviours that are encouraged by the developed transport system, automated household chores, and indoor entertainment \citep{Malik2013}.

Urbanisation by itself cannot be accounted for the lack of exercise in the population, but it is true that urbanisation makes the bar higher for many people to take up the recommended level of fitness and maintain it. \\

\noindent
The third factor is the income and socioeconomic status of the population.
As the average income increases, more people are able to buy food and are likely to take up the sedentary lifestyle.
Clearly, these behavioural changes will increase the likelihood of becoming obese.

From this, one would expect the high-income group to have the largest impact from obesity, but on the contrary to this expectation, the biggest impact from obesity is seen in the low- and middle-income groups of the population \citep{Malik2013}.
As mentioned briefly earlier, access to the developed health care system will allow weight maintenance of the population, but this is likely to be of most benefit for the high-income group in the population.
The reason for this is, quite simply, the cost associated with the visit to the health care system, and therefore high-income group is more likely to make a consistent and periodic visit than the low or middle-income group of the population \citep{Malik2013}.

So, for the low- and middle-income groups, the rise in average income in these groups allow the people to have access to food and activities that promotes sedentary bahaviours, but the limited access to the health care system, education and recreational activities that promote physical activites ultimately leads to positive energy balance and obesity \citep{Malik2013}.
In contrast, the high-income group of the population have better access to the facilities that promote weight maintenance, thus have less of an impact from obesity compared with the low- and middle-income groups of the population.\\

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet made by the population.
The amount of low-quality food have increased significantly in many rapidly growing countries, as these high-energy, low-nutritional food are cheaper and more profitible than the natural produce that have higher nutritional value \citep{Kearney2010}.
As a result, more people tend to purchase these low-quality food more often, and consume more energy than they are required.

However, many people eat responsibly and avoid these low-quality diet and prevent overconsumption of such food, but the overconsumption of these food is not a big problem as such, rather the overall quality of the food \citep{Malik2013}.
These food are usually high in refined sugar and unhealthy fat, highly processed, contain very little nutritional value and are low in fibre.
As a result, consumption of these food increases the overall energy intake and achieve no nutritional benefits from the food.

Whether it is by choice or not, consumption of these low-quality diet leads to obesity and obesity-related diseases. \\

@@

\subsection{Impact of obesity}
\label{sub:impact_of_obesity}

As mentioned at the beginning of the current section, obesity has a devastating effect on the health of the population in a global scale.

Overweight and obesity have been a risk factor for many diseases, including type 2 diabetes, cardiovascular diseases, hypertension, and many types of cancers \citep{Franks2010, Guh2009, Yach2006}.
As \citet{Yach2006} mentions in their paper, ``overweight and obesity have become to diabetes what tobacco is to lung cancer'', and it is important to understand that obesity has significant risks and comorbidities associated with it.

Although adulthood obesity is clinically important for risk assessment of diseases, childhood obesity has been focussed more heavily in recent years,  as it has greater public health implications.
There are many immediate consequences that are related to childhood obesity, but the diseases that develop as these children grow up are more critical than the earlier effects.

In the paper written by \citet{Must1999}, they reviewed many of the clinical studies done in the 1900s and summarised the risks associated with childhood obesity.
Among the many risks associated with obesity, obese children, compared to lean children, had over 8.5-fold increased risk of developing hypertension as adults \citep{Must1999}.
On top of this, the relative risks for all-cause mortality and coronary heart disease-specific mortality were 1.5 and 2.5, respectively \citep{Must1999}.

>>>>

Obesity is defined as an abnormal or excessive fat accumulation that may impair health of that individual \citep{Garrow1988}.
One common and widely used approach to categorise individuals is by measuring the \gls{bmi} of the individual.
\gls{bmi} is a measurement based on the weight-to-height ratio of an individual that is used by clinicians and epidemiologists to classify adults into underweight, normal weight, overweight or obese categories.
The unit of \gls{bmi} is defined as the individual's weight in kilograms per square of the height in meters (kg/m$^2$).

@@

In addition to this, the worldwide prevalence of childhood overweight and obesity has been increasing steadily since 2000 \citep{WHO2014}.
Furthermore, the prevalence of overweight in children under 5 years was estimated to reach from 6.3\% in 2013 to 11\% by 2025 if the current trend continued \citep{WHO2014}.
The current obesity status of the adult population is bad already, but the fact that more of the younger population who are overweight and obese poses a much greater risk for the health of the population.

@@

% Until these terrible trends stop, and even after the trends stop, the world will need a plan to live along with this ongoing global epidemic of obesity and its associated diseases.

@@

Obesity is caused by continuous intake of food without expending all of the energy gained.
The key to the problem is the control of food intake and energy expenditure, and how they are regulated in your body.
The role of hypothalamus is central to the control of satiety and many mutations that cause obesity affects the satiety signals to and/or from hypothalamus.
The hypothalamus receives both nueronal and hormonal inputs from the body and propagates the signal to the downstream neurons that ultimately affect the food intake of the individual \citep{Bell2005, Spiegelman2001}.

There are two types of neurons in the arcuate nucleus (located in the hypothalamus): orexogenic and anorexogenic neurons.
Orexogenic neurons are responsible for the promotion of food intake and reducing energy expenditure, whereas the anorexogenic neurons have the opposite effect \citep{Barsh2002}.
When stimulated by, for example, endocrine signals, these two different types of neurons act on the downstream neurons to promote or reduce food intake and energy expenditure.

Leptin-melanocortin pathway is the main pathway in which the level of satiety is controlled and regulated \citep{Spiegelman2001}.
In this pathway, both the orexogenic and anorexogenic neurons (located in the arcuate nucleus of the hypothalamus) have crucial roles in controlling the satiety of the individual, and therefore their eating behaviour \citep{Barsh2002,Bell2005}.
When a satiety-controlling hormone such as leptin reaches the arcuate nucleus region of the hypothalamus, it can stimulate or inhibit orexogenic, anorexogenic, or both orexogenic and anorexogenic neurons.
Depending on which neurons are stimulated or inhibited, the hormone will ultimately alter the satiety level of the individual.

Though there are many hormones that regulate satiety, only leptin and insulin will be covered here.
Leptin gene was first discovered by \citet{Zhang1994} and the discovery of the leptin receptor gene was followed shortly after by \citet{Tartaglia1995}.
Together, the identification of the leptin and leptin receptor genes was a major break through in the field of obesity research.

Leptin is a hormone that signals satiety and reduces food intake, and is secreted mainly by the white adipose tissue \citep{Moustafa2013,Zhang1994}.
The circulating concentration of leptin in the body is proportional to the body fat stores \citep{Barsh2002, Moustafa2013}.
Leptin signals through the \gls{jak}/\gls{stat} pathway via the long form of the leptin receptor that is present in high expression in the hypothalamus \citep{Ghilardi1996,Lee1996}.
Depending on the type of neurons the leptin receptor is expressed, leptin stimulate or inhibit these neurons and ultimately produces an anorexogenic signal to the downstream effector neurons \citep{Bell2005}.

Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.
Briefly, when insulin binds to the insulin receptor, \gls{irs} protein family is recruited and phosphorylated by the insulin receptor's intrinsic tyrosine kinase activity \citep{Saltiel2002}.
The phosphorylated \gls{irs} protein then activates \gls{pi3k}, which in turn activates its downstream targets, causing a rapid signal cascade through the cell \citep{Saltiel2002}.

The evidence of insulin's involvement in the satiety control was not particularly clear even though there were strong evidence of obesity with neuron-specific deletion of insulin receptor, and that the insulin level, like leptin, was proportional to the fat mass also suggested the role of insulin in satiety and body weight control \citep{Barsh2002, Bruning2000, Woods1979}.
This was perhaps due to the fact that leptin and insulin used two different signalling pathways in the cell; leptin used the \gls{jak}/\gls{stat} signalling pathway, whereas insulin used the \gls{pi3k} pathway for signalling \citep{Ghilardi1996}.
This was puzzling to the researchers as there seemed to be no converging point of the two hromones in these pathways.

However, leptin, and subsequently insulin, was shown to activate ATP-dep\-endent K$^+$ channel in glucose-responsive neurons in the hypothalamus \citep{Spanswick1997, Spanswick2000}.
The activation of K$^+$ channel provided evidence for the two pathways to act similarly on the cell, at least for an acute response, suggesting a convergence in the pathway response by the two hormones, and therefore their role in satiety control.

Satiety control is crucial in order to manage  and maintain the body weight in a healthy state.
As described above, there are many components that regulate satiety and disruption of any part of this satiety controlling pathway can encourage the development of obesity.

@@

There are many environmental factors associated with the global rise in obesity.
Even though these environmental factors are probably the most significant contributor to the current global obesity epidemic, there are some individual-level, genetic factors that contribute to the overall increase in the proportion of the population that are obese.

There is much evidence of obesity being caused by individual-level genetic factors that make some individuals more predisposed to obesity than others.
Generally speaking, there are two classes of genetically-driven obesity: monogenic obesity and polygenic obesity \citep{Moustafa2013}. \\

\noindent
Monogenic obesity is where a single mutation in one of the genes that is directly involved in the satiety controlling pathway causes severe obesity in that individual.
Since these mutations are usually directly related to the key constituents in the pathway mentioned earlier (\cref{sub:physiological_mechanism_of_obesity}), the resulting phenotype from the mutation causes severe early-onset obesity.
However, although these mutations cause a devastating effect on the individual carrying the mutation, these mutations occur very rarely in the population.
% With that said though, the identification of these mutations have shed light on the mechanisms in which obesity is developed and it is worth mentioning some of these mutations to highlight the importance of the components involved in the obesity pathway.

An example of a mutation that causes severe early-onset obesity is a mutation in the leptin gene.
\citet{Montague1997} found a single nucleotide deletion mutation at position 133 of the leptin gene in children with early-onset obesity.
They further showed that the mutation caused a frameshift mutation in the protein, resulting in an inactive form of leptin that was not able to be secreted \citep{Montague1997}.
As a result, children with this mutation was constantly hungry due to the lack of anorexogenic signals, and became obese at a very early stage of their lives.
\\

% In close relation to this mutation is the mutation in the leptin receptor gene.
% \citet{Clement1998} have discovered a single nucleotide substitution mutation that led to the leptin receptor transcript that skipped exon 16, leading to a form of the receptor with no transmembrane or intracellular domain.
% Individuals with this rare mutation showed extreme hyperphagia and symptoms of early-onset obesity, even though their circulating leptin levels were present abundantly \citep{Clement1998}.

% The next couple of mutations are associated with the synthesis and the processing of \gls{pomc}.
% \citet{Krude1998} found single nucleotide mutations in the exonic region of the \gls{pomc} gene that affected the transcription of the $\alpha$-\gls{msh} region (and some other regions) of \gls{pomc}.
% \citet{Jackson1997} identified a mutation in the \gls{pc1}, an enzyme responsible for the processing of many prohormones and neuropeptides, including \gls{pomc}.
% In either case, the mutation resulted in the lack of $\alpha$-\gls{msh} in the neurons for satiety signalling and caused severe early-onset obesity.

% As mentioned earlier, even though these mutations are very rare and affects only those individuals that have one of these mutations, it had a profound impact in the field of obesity research and contributed significantly to the knowledge of the mechanism of how obesity develops.

\noindent
Polygenic obesity is where a combination of variants in multiple genes or multiple regions of the genome, together with environmental factors, causes obesity in the individual \citep{Moustafa2013}.
Unlike in monogenic obesity where a single mutation in a gene causes severe obesity, the variants in some of the genes or genomic regions involved in polygenic obesity have little effect on the individual's obesity status by itself, but in combination with many other variants and together with environmental factors, it has a serious obesogenic effect on the individual.

% Known as the ``thrifty gene'' hypothesis, \citet{Neel1962} suggested that the genes that were important in obesity have been around in the population for many generations, as it would have had a selective advantage in an environment where the population experienced starvation more frequently than the current generation.
% However, as food became more accessible, a subset of the population who were particularly good at storing fat and survive the starvation period ``overreacted'' to this rapid change in the environment \citep{Bell2005, Spiegelman2001}.
% These observations in the rise in obesity in subsets of population cannot be explained simply by external factors alone, and there is a significant genetic component involved in this phenomenon \citep{Bell2005}.

@@

% Discovery of the \gls{fto} gene has lead to extensive research on the gene, and the mechanism of action by the \gls{fto} variant has been recently uncovered  from these efforts \citep{Claussnitzer2015a,Smemo2014a}.
% The association between obesity and genetic variations, and their mechanisms that lead to obesity, has not been fully elucidated due to its complexity, but it may not be long before they are fully uncovered.

@@

Even though some individual-level factors are involved with obesity, it is clear that these individual-level factors cannot be accounted for the global epidemic of obesity that the world currently observes.
For this reason, obesity is thought to be caused mainly by the environmental factors that act at a population-level.\\

\noindent
The first key factor that contirbutes to the global rise in the proportion of the population that is obese is the availability and abundance of certain food in the country.
With the help from government trade policies, food and other goods have become easier to trade between the country, helping the economic growth of many countries around the world \citep{Kearney2010}.
This led to greater abundance of food in general, greater number of choices of food and shifted the overall nutritional status of the country \citep{Malik2013}.
This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in population-wide rise in obesity.
% This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in a different, much larger problem -- obesity.

As an example, in the \gls{usa}, the cost of corn and soy is low due to the fact that they are the raw ingredients for most processed food and beverages, such as high fructose corn syrups used to sweeten many soft drinks in the \gls{usa} \citep{Malik2013}.
Moreover, corn and soy are also the main food for the livestock, which results in lower prices for meat \citep{Malik2013}.
On the other hand, the prices of fruits and vegetables remain expensive due to the lack of support by the government to lower the cost associated with the production \citep{Malik2013}.

As a result, more people are inclined to consume food that are cheap, have little nutritional value and high in energy, than the food that are expensive, nutritional and healthy alternatives.
Thus, the population is more likely to become obese by making poor food choice.\\

\noindent
The second factor to consider is the behavioural changes led by the urbanisation of the population.
% Urbanisation is defined as the gradual increase in the proportion of people living in urban areas.
As more people take up urban lifestyle, they are exposed to the new environment where there is a better range of food selection, as well as technological and mechanical advancement in transport and other daily chores that may not be available in rural areas.

Although there are many advantages involved with urbanisation, such as access to developed health care systems, education and advanced technologies, the lifestyle change also impose negative health behaviour that ultimately lead to positive energy balance and therefore obesity \citep{Malik2013}.
Lack of physical activity is one of the obvious components that is linked with the urbanisation of the population.
% Currently, the recommended amount of physical activity to keep an individual fit and healthy is $\geq$ 150 min of moderate-intensity aerobic physical activity per week, or $\geq$ 30 min of physical activity on most days of the week \citep{Pate1995, WHO2010}.
In many urban cities, the recommended level of physical exercise is difficult to achieve and maintain due to the shift towards the sedentary behaviours that are encouraged by the developed transport system, automated household chores, and indoor entertainment \citep{Malik2013}.
\\
% Urbanisation by itself cannot be accounted for the lack of exercise in the population, but it is true that urbanisation makes the bar higher for many people to take up the recommended level of fitness and maintain it. \\

\noindent
The last factor to be mentioned is the income and socioeconomic status of the population.
As the average income increases, more people are able to buy food and are likely to take up the sedentary lifestyle.

From this, one would expect the high-income group to have the largest impact from obesity, but on the contrary to this expectation, the biggest impact from obesity is seen in the low- and middle-income groups of the population \citep{Malik2013}.
Access to the developed health care system will allow weight maintenance of the population, but this is likely to be of most benefit for the high-income group in the population.
The reason for this, quite simply, is the cost associated with the visit to the health care system, as high-income group is more likely to make a consistent and periodic visit than the low or middle-income group of the population \citep{Malik2013}.

So, for the low- and middle-income groups, the rise in average income in these groups allow the people to have access to food and activities that promotes sedentary bahaviours, but the limited access to the health care system, education and recreational activities that promote physical activites ultimately lead to positive energy balance \citep{Malik2013}.
In contrast, the high-income group of the population have better access to the facilities that promote weight maintenance, thus have less of an impact compared with the low- and middle-income groups of the population.
\\

% \noindent
% The last factor, which ties in strongly with the first key factor, is the choice of diet made by the population.
% The amount of low-quality food have increased significantly in many rapidly growing countries, as these high-energy, low-nutritional food are cheaper and more profitible than the natural produce that have higher nutritional value \citep{Kearney2010}.
% As a result, more people tend to purchase these low-quality food more often, and consume more energy than they are required.

% However, many people eat responsibly and avoid these low-quality diet and prevent overconsumption of such food, but the overconsumption of these food is not a big problem as such, rather the overall quality of the food \citep{Malik2013}.
% These food are usually high in refined sugar and unhealthy fat, highly processed, contain very little nutritional value and are low in fibre.
% As a result, consumption of these food increases the overall energy intake and achieve no nutritional benefits from the food.

% Whether it is by choice or not, consumption of these low-quality diet leads to obesity and obesity-related diseases. \\

@@

% \subsection{Impact of obesity}
% \label{sub:impact_of_obesity}

% As mentioned at the beginning of the current section, obesity has a devastating effect on the health of the population in a global scale.
% Overweight and obesity have been a risk factor for many diseases, including type 2 diabetes, cardiovascular diseases, hypertension, and many types of cancers \citep{Franks2010, Guh2009, Yach2006}.
% As \citet{Yach2006} mentions in their paper, ``overweight and obesity have become to diabetes what tobacco is to lung cancer'', and it is important to understand that obesity has significant risks and comorbidities associated with it.

% Although adulthood obesity is clinically important for risk assessment of diseases, childhood obesity has been focussed more heavily in recent years,  as it has greater public health implications.
% There are many immediate consequences that are related to childhood obesity, but the diseases that develop as these children grow up are more critical than the earlier effects.
% A paper by \citet{Must1999} reviewed many of the clinical studies done in the last several decades and summarised the risks associated with childhood obesity.
% Among the many risks associated with obesity, obese children, compared to lean children, had over 8.5-fold increased risk of developing hypertension as adults \citep{Must1999}.
% On top of this, the relative risks for all-cause mortality and coronary heart disease-specific mortality were 1.5 and 2.5, respectively \citep{Must1999}.
